\mytitile\\~

### 2020-04-16 document.tex
restored table 1

>>>>

\begin{table}
	\begin{ruledtabular}
		\begin{tabular}{rll}
			Parameter & Transmon 1  & Transmon 2\\\hline
			$\omega/2\pi$ [GHz] & 5.12 - 6.3  & 4 - 5.45\\
			$\alpha/2\pi$ [MHz] & -220 & -220 \\
			$T_1$ [$\mu$s]  & 6.82 &  4.41 \\
			$T_2^*$ [$\mu$s]  & 5.14  &  3.33\\\hline
			$J/2\pi$ [MHz] &\multicolumn{2}{c}{8} 
		\end{tabular}
	\end{ruledtabular}
	\caption{SAM model parameters. Transmons are only 
		different in the frequency tuning range and 
		coherence times measured in the lower sweet 
		spot for the 1\textsuperscript{st} one and in 
		the higher sweet spot for the 
		2\textsuperscript{nd}. The coupling strength 
		$J$ depends on the transmon frequencies and 
		is specified here for $\omega_1/2\pi = 
		\omega_2/2\pi = 5.32$ GHz.}
	\label{tab:parameters}
\end{table}
